---
title: "Productivity & GDP Data Cleaning"
author: "Cam Fraser"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Initial Exploration

Here is documentation of the 8 initial datasets, with initial exploration and data 
cleaning. <br>
New data sets will be created from these data sets and saved as new files with 
meaningful names!


# Looking at data before importing

8 datasets were initially supplied for this project, here's a summary of each

---

# Exports by business size

`Exports by business size - OECD.xlsx` 
<br>
1 sheet with the following variables:

* Location - countries with the first 3 letters to denote
* Indicator - one factor "EXPBSNS" meaning expenses
* Subject - number of employees (All, 0-9, 10-49, 50-249, 250 or more)
* Measure - one factor "MLN_USD" which is the currency used to measure
* Frequency - one factor "A" meaning whole year/all year
* Time - which year the row relates to (2008 - 2017)
* Value - value of MLN_USD for that year (if next column has E then it's an estimate)

---

# UK GDP Estimates

`UK GDP Estimates - Time Series.xlsx`
<br>
1 sheet with alot of data within it

Multiple variables but is a time series data set from 1946 - 2018, with it also 
split by quarter (but appended row)
<br>
Might be hard to use 
<br>
This data is split into different variables that lead to GDP

---

# UK Labour Productivity 

`Uk Labour Productivity - Time Series.xlxs`
<br>
1 sheet with a lot of data within it

Multiple variables but is a time series data set from 1946 - 2018, with it also split by quarter (but appended row)
<br>
Might be hard to use (like above)
<br>
This data is split into different variables that lead to Productivity

---

# Global Competitiveness Dataset

`Global Competitiveness Dataset.xlxs`
<br>
4 sheets

* Terms and conditions in "About this dataset"
* Main dataset in "Data"
  * countries are variables, each row is global competitiveness index per country 
  for 2018, and 2017 forecast
  * some hidden columns with meanings in the next sheet
* Meaning for each row in "Meta Data"
* Countries and their codes in "Entities"

---

# Global Financial Development

`Global Financial Development.xlxs`
<br>
2 sheets with the following info in them:

* "Definitions and Sources" is a sheet explaining each variable
* "Data - July 2018" is a sheet with a lot of info on GDP for different countries
  * Variables of interest will be population total `SP.POP.TOTL`, GDP per capita `NY.GDP.PCAP.KD`

---

# Growth Of Lending - Individuals

`GrowthOfLending_Individuals.xlxs`
<br>
1 sheet with following info:

* Monthly growth rates (for 1 month, 3 months, 6 months, 12 months) not leading to individuals
* Data taken from Bank of England

---

# UK Public Service Productivity

`UK Public Service Productivity.xlsx`
<br>
4 sheets with the following info:

* sheet explaining what's contained in the spreadsheet "Content"
* UK annual productivity, inputs and outputs form 1997 to 2017 "Annual PSP"
* UK quarterly product, inputs and outputs for 2017 to 2018 "Quarterly PSP"
* Revisions for quarterly data from 2011 to 2017 for each income, output and 
product "Revisions to PSP"

---

# Growth of Output

`Growth of Output.xlxs`
<br>
3 sheets with the following info:

* countries and their GDP growth rates based on the local currency from 1961 - 2017 (when the information is available)
* Information on each countries income group, notes on main industries, country codes "Metadata - Countries"
* Explanation of what the data is "Metadata - indicators"

---
---

# Data Cleaning

Here will perform any steps to clean data/create new data sets for initial exploration into trends of GDP and Productivity

# Exports by business size - OECD.xlsx

```{r}
library(reticulate)
```


```{python}
use_condaenv("python")
```


```{python}
import pandas as pd
import numpy as np
```






